Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-14 paper/responseToReviewers.tex

\item \emph{The used classifier is not the same (from unsupervised GMM to supervised SVM)}
This is an important point and we have included results for MFCCs using a linear SVM. However, we point out that the GMM is also supervised, although it is trained using a generative objective as opposed to a discriminative one, which is the case for the SVM.

\item \emph{The paper reads like a recipe for the specific task without justifications, insights or proofs of the different given definitions and statements.}
We justify the cluster-based representation with results from cognitive psychology. The use of the scattering transform is justified with invariance conditions of the tasks. Where necessary, the proofs and evidence are provided in references. Again, the lack of specificity of this point makes it hard to address, but as stated above, we have reworked the whole paper to hopefully make our argument clearer.

\item \emph{The dataset is not well presented since the classes seem to represent stationary noises such as car/tram/train}
While these scenes definitely have a stationary component, such as for the car, tram, train, metro station, and bus classes. This is not sufficient to classify them, since this stationary signal is very similar for these classes. This is why the cluster-based hierarchical representation that we propose is necessary in that it allows the system to pick out the distinct non-stationary components that discriminate between the classes.

\item \emph{"Recordings may be shifted locally 
without affecting their perception and therefore such shifts do not convey any information about the class" this is false. Rather say that application of time shift should not change the representation since it doesn't change the class belonging in this context and thus imposing time shift invariance will improve robustness.}
The reviewer is correct that this is not true as stated. Our meaning is indeed what he/she describes and the text has been changed to reflect this.

@@

\item \emph{It is then explained that the features are stable to time warping yet the justification is for pitch variations which are frequency-warping}
The justification of pitch variation is indeed a frequency-warping, but can be written as a time-warping. Indeed, a signal that is slightly compressed or dilated locally will have its pitch transposed up or down.

\item \emph{The scattering network is defined with an infinite cascade of transform yet it is enough to compute two layers, why?}
For the time scales considered in this paper, the first two orders are sufficient to describe the sound events present in the signals. This has been made clearer in the text.

\item \emph{It is never specified what are the signals frequency sampling which we have to deduce to be 44100 Hz from line 9 page 3 "20kHz close to the Nyquist frequency of the audio recordings".}

\item \emph{"Wavelet scalogram" is used along all the paper but scalogram is only defined for wavelets since 
it is a scale-o-gram.}
This is true, but for readers less familiar with the terminology, we have opted to use this more redundant expression to express the fact that these derive from wavelet decompositions.

### 2016-12-14 paper/structureScene.tex
answer to ja

We define second-order wavelets $\boldsymbol{\psi_{\gamma_2}}(t)$ in the same way as the first-order wavelets, but with parameters $\xi_2$, $J_2$, and $Q_2$ and so have center frequencies $2^{-\gamma_2/Q_2}\xi_2$ for $\gamma_2$ taking values between $0$ and $(J_2 \times Q_2 - 1)$. While this abuses notation slightly, the identity of the wavelets should be clear from context.
The amplitude modulation spectrum resulting from a wavelet modulus decomposition using these second-order wavelets is then
\begin{equation}
\boldsymbol{x_2}(t,\gamma_1,\gamma_2) =
\vert \boldsymbol{x_1} \ast \boldsymbol{\psi_{\gamma_2}} \vert(t,\gamma_1).
\end{equation}
In the sequel, we set $\xi_2$ to $2.5\,\mathrm{kHz}$, $Q_2$ to $1$, and $J_2$ to $12$. \ja{Why is $\xi_2 \neq \xi_1$?} Lastly, the low-pass filter $\phi(t)$ is applied to $\boldsymbol{x_2}$ to guarantee local invariance to time-shifting, which yields
\begin{equation}
\mathbf{S_2}\boldsymbol{x}(t,\gamma_1,\gamma_2) =
(\boldsymbol{x_2}(\cdot,\gamma_1,\gamma_2) \ast \phi)(t).
\end{equation}

@@

Logarithmic compression provides a small, albeit consistent boost to acoustic scene classification over all folds in the DCASE 2013 private dataset.
Indeed, as discussed in subsection \ref{sec:logcomp}, and observed in Figure \ref{fig:compression}, the statistical assumption of normality for scattering coefficients is only approximately satisfied once mapped to a logarithmic, decibel-like scale. \ja{Isn't this why we also standardize the coefficients?}
This transformation improves the discriminative power of the SVMs trained on scattering coefficients, regardless of the chosen temporal integration strategy (early or late) and the inner product kernel (linear or Gaussian RBF).
Again, this is in accordance with our previous findings on acoustic scene similarity retrieval, which are reported in Figure \ref{fig:ASS_2}.

>>>>

We define second-order wavelets $\boldsymbol{\psi_{\gamma_2}}(t)$ in the same way as the first-order wavelets, but with parameters $\xi_2$, $J_2$, and $Q_2$ and so have center frequencies $2^{-\gamma_2/Q_2}\xi_2$ for $\gamma_2$ taking values between $0$ and $(J_2 \times Q_2 - 1)$. While this abuses notation slightly, the identity of the wavelets should be clear from context.
The amplitude modulation spectrum resulting from a wavelet modulus decomposition using these second-order wavelets is then
\begin{equation}
\boldsymbol{x_2}(t,\gamma_1,\gamma_2) =
\vert \boldsymbol{x_1} \ast \boldsymbol{\psi_{\gamma_2}} \vert(t,\gamma_1).
\end{equation}
In the sequel, we set $\xi_2$ to $2.5\,\mathrm{kHz}$, $Q_2$ to $1$, and $J_2$ to $12$. \ja{Why is $\xi_2 \neq \xi_1$?} \vl{$\xi_2 = \xi_1 / 8$ because $Q_1=8$}Lastly, the low-pass filter $\phi(t)$ is applied to $\boldsymbol{x_2}$ to guarantee local invariance to time-shifting, which yields
\begin{equation}
\mathbf{S_2}\boldsymbol{x}(t,\gamma_1,\gamma_2) =
(\boldsymbol{x_2}(\cdot,\gamma_1,\gamma_2) \ast \phi)(t).
\end{equation}

@@

Logarithmic compression provides a small, albeit consistent boost to acoustic scene classification over all folds in the DCASE 2013 private dataset.
Indeed, as discussed in subsection \ref{sec:logcomp}, and observed in Figure \ref{fig:compression}, the statistical assumption of normality for scattering coefficients is only approximately satisfied once mapped to a logarithmic, decibel-like scale. \ja{Isn't this why we also standardize the coefficients?} \vl{No, standardization does not affect skewness, unlike log compression}
This transformation improves the discriminative power of the SVMs trained on scattering coefficients, regardless of the chosen temporal integration strategy (early or late) and the inner product kernel (linear or Gaussian RBF).
Again, this is in accordance with our previous findings on acoustic scene similarity retrieval, which are reported in Figure \ref{fig:ASS_2}.
